A Study on Online Sequential Learning using Bandits

### 2017-12-11 Chapter6/mainresult.tex
Latest on 11/12/2017

\begin{theorem}
The expected cumulative regret of ImpCPD algorithm is upper bounded by,
\begin{align*}
\E[R_t] &\leq \sum_{i = 1}^K\sum_{j=1}^{G}\bigg[ 1 
%%%%%%%%%%
+ \dfrac{4T\Delta^{opt}_{i,c_j}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha +1}}{(\Delta^{opt}_{i,c_j})^{4\alpha +2}}
%%%%%%%%%%
+ \Delta^{opt}_{i,c_j} + \dfrac{4\log(\psi T(\Delta^{opt}_{i,c_j})^4)}{2(\Delta^{opt}_{i,c_j})}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
& + \dfrac{2T\Delta^{opt}_{i,c_{j+1}}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha + 1}}{(\Delta^{chg}_{i,c_j})^{4\alpha + 2}}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
&+ \Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2\Delta^{chg}_{\epsilon_0,c_j}} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{i,c_j})^2}
\bigg]
\end{align*}

where $\alpha,\psi$ are exploration parameters and $M=\dfrac{1}{2}\log_{2}\dfrac{T}{e}$.
\end{theorem}

@@

\textbf{Step 2.(Define an optimality stopping phase $m_i$):} We define an optimality stopping phase $m_i$ for a sub-optimal arm $i\in\A$ as the first phase after which the arm $i$ is no longer pulled such that,

\begin{align*}
m_i = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{opt}_{i,c_j}}{4} \right\rbrace
\end{align*}

\textbf{Step 3.(Define a changepoint stopping phase $p_i$):} We define a changepoint stopping phase $p_i$ for an arm $i\in\A$ such that it is the first phase when the changepoint is detected such that,

\begin{align*}
p_i = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{chg}_{i,c_j}}{4} \right\rbrace
\end{align*}

\textbf{Step 4.(Regret for sub-optimal arm $i$ being pulled after $m_i$-th phase):} Note, that on or after the $m_i$-th phase a sub-optimal arm $i$ is not pulled anymore if these four conditions hold,

@@

Also, in the $m_i$-th phase if $n_i \geq \ell_{m_i} = \dfrac{\log(\psi T\epsilon_{m_i}^2)}{2\epsilon_{m_i}}$ then we can show that,
\begin{align*}
s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_i}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_i}^2)}{2\ell_{m_i}}} \leq \sqrt{\alpha\epsilon_{m_i}\dfrac{\log(\psi T\epsilon_{m_i}^2)}{\log(\psi T\epsilon_{m_i}^2)}} \leq \dfrac{\Delta^{opt}_{i,c_j}}{4}.
\end{align*}

If indeed the four conditions in equation \ref{eq:arm-pull-opt} hold then we can show that in the $m_i$-th phase,

\begin{align*}
\hat{r}_{i,c_j} + s_i \leq \hat{r}_{i,c_j} + 4s_i - 2s_i \leq \hat{r}_{i,c_j} + \Delta^{opt}_{i,c_j} - 2s_i \leq \hat{r}_{i*,c_j} - 2s_{i*} \leq \hat{r}_{i*,c_j} - s_{i*}
\end{align*}

Hence, the sub-optimal arm $i$ is no longer pulled on or after the $m_i$-th phase. Therefore, to bound the number of pulls of the sub-optimal arm $i$, we need to bound the probability of the complementary of the four events in equation \ref{eq:arm-pull-chg}.

@@

\begin{align*}
\sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace \hat{r}_{i,c_j} \geq  r_{i,c_j} + s_i \rbrace &\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\exp\left(-2s_i^2n_i \right)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\exp\left(-2\dfrac{\alpha\log(\psi T\epsilon_{m_i}^2)}{2n_i}n_i \right)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\dfrac{1}{\psi T\epsilon_{m_i}^2} \leq \sum_{m=0}^{m_i}\dfrac{\log(\psi T\epsilon_{m_i}^2)}{2\epsilon_{m_i}}\dfrac{1}{(\psi T\epsilon_{m_i}^2)^{\alpha}} = \dfrac{\log(\psi T)}{2(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
\end{align*}

@@

\begin{align*}
\sum_{m=0}^{m_i}\sum_{n_{i*} =1}^{\ell_{m_i}}\Pb\lbrace \hat{r}_{i*,c_j} \leq  r_{i*,c_j} - s_{i*} \rbrace &\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\exp\left(-2(s_{i*})^2n_{i*} \right)\leq \dfrac{\log(\psi T)}{2(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
\end{align*}

@@

\begin{align*}
\sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace.
\end{align*}

But the event $\hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_i$ is possible only when the following three events occur, $\hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} , \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i$ and $r_{i*}-r_{i} < 2s_i $. But the third event will not happen for $n_i\geq \ell_{m_i}$. Proceeding as before, we can show that the probability of the remaining two events is bounded by,

\begin{align*}
&\sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
&\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\left( \Pb\lbrace \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i \rbrace \bigcup \Pb\lbrace \hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} \rbrace \right)\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\dfrac{\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha + 1}}.
\end{align*}

Finally for the fourth event in equation \ref{eq:arm-pull-opt}, we can bound the probability of its complementary event by following the same steps as above,

\begin{align*}
\sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace r_{i,c_j} + s_i > r_{i*,c_j} + s_{i*} \rbrace \leq \dfrac{\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
\end{align*}

Combining the above four cases we can bound the probability that a sub-optimal arm $i$ will no longer be pulled on or after the $m_i$-th phase by,

\begin{align*}
\dfrac{4\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
\end{align*}

Bounding this trivially by $T\Delta^{opt}_{i,c_j}$ for each arm $i\in\A$ we get the regret suffered for arm $i$ after the $m_i$-th phase  as,

\begin{align*}
\sum_{i\in\A}\left(\dfrac{4T\Delta^{opt}_{i,c_j}\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}\right) \leq \sum_{i\in\A}\left(\dfrac{4T\Delta^{opt}_{i,c_j}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha +1}}{(\Delta^{opt}_{i,c_j})^{4\alpha +2}}\right).
\end{align*}

\textbf{Step 5.(Regret for pulling the sub-optimal arm $i$ on or before $m_i$-th phase):} Either a sub-optimal arm gets pulled $\ell_{m_i}$ number of times till the $m_i$-th phase and after that the probability of it getting pulled is exponentially low (as shown in \textbf{step 4}). Hence, the number of times a sub-optimal arm $i$ is pulled till the $m_i$-th phase is given by,

\begin{align*}
\ell_{m_i} = \left\lceil \dfrac{\log(\psi T\epsilon_{m_i}^2)}{2\epsilon_{m_i}} \right\rceil
\end{align*}

@@

\begin{align*}
\sum_{i\in\A}\Delta^{opt}_{i,c_j}\left\lceil \dfrac{\log(\psi T\epsilon_{m_i}^2)}{2\epsilon_{m_i}} \right\rceil < \Delta^{opt}_{i,c_j}\left[ 1 + \dfrac{\log(\psi T\epsilon_{m_i}^2)}{2\epsilon_{m_i}} \right] \leq \Delta^{opt}_{i,c_j}\left[ 1 + \dfrac{4\log(\psi T(\Delta^{opt}_{i,c_j})^4)}{2(\Delta^{opt}_{i,c_j})^2}\right].
\end{align*}

\textbf{Step 6.(Regret for not detecting changepoint $c_{j}$ for arm $i$ after the $p_{i}$-th phase):} Proceeding similarly as in \textbf{step 4} we can show that in the $p_i$-th phase for an arm $i$ if $n_{i}\geq\ell_{p_i}$ then,

\begin{align*}
s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_i}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_i}^2)}{2\ell_{p_i}}} \leq \sqrt{\alpha\epsilon_{p_i}\dfrac{\log(\psi T\epsilon_{p_i}^2)}{\log(\psi T\epsilon_{p_i}^2)}} \leq \dfrac{\Delta^{chg}_{i,c_j}}{4}.
\end{align*}

@@

Indeed, we can show that if there is a changepoint at $c_j$ such that $r_{i,c_{j-1}} < r_{i,c_j}$ and if the first conditions in equation \ref{eq:arm-pull-chg} hold  in the $p_i$-th phase then,

\begin{align*}
\hat{r}_{i,c_{j-1}} + s_{i} \leq \hat{r}_{i,c_{j-1}} + 4s_{i} - 2s_{i} \leq \hat{r}_{i,c_{j-1}} + \Delta^{chg}_{i,c_j} -2s_{i} \leq \hat{r}_{i,c_{j}} - 2s_i \leq \hat{r}_{i,c_{j}} - s_i.
\end{align*}

Conversely, for the case $r_{i,c_{j-1}} > r_{i,c_j}$ the second condition will hold for the $p_i$-th phase. Now, to bound the regret we need to bound the probability of the complementary of these two events. For the complementary of the first event in equation \ref{eq:arm-pull-chg} by using Chernoff-Hoeffding bound we can show that,

\begin{align*}
&\sum_{m=0}^{p_i}\sum_{n_i=1}^{\ell_{p_i}}\Pb\lbrace \hat{r}_{i,c_{j-1}} \geq  r_{i,c_{j-1}} + s_i \rbrace \leq \sum_{m=0}^{p_i}\sum_{n_i=1}^{\ell_{p_i}}\exp\left(-2s_i^2n_i \right)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\leq \sum_{m=0}^{p_i}\sum_{n_i=1}^{\ell_{p_i}}\exp\left(-2\dfrac{\alpha\log(\psi T\epsilon_{p_i}^2)}{2n_i}n_i \right)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq \sum_{m=0}^{p_i}\sum_{n_i=1}^{\ell_{p_i}}\dfrac{1}{\psi T\epsilon_{p_i}^2} \leq \sum_{m=0}^{p_i}\dfrac{\log(\psi T\epsilon_{p_i}^2)}{2\epsilon_{p_i}}\dfrac{1}{(\psi T)^{\alpha}\epsilon_{p_i}^2} = \dfrac{\log(\psi T)}{2(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_i}^{2\alpha + 1}}.
\end{align*}

@@

\begin{align*}
\sum_{m=0}^{p_i}\sum_{n_i=\ell_{p_{i-1}}}^{\ell_{p_i}}\Pb\lbrace \hat{r}_{i,c_j} \leq  r_{i,c_j} - s_i \rbrace &\leq \sum_{m=0}^{p_i}\sum_{n_i=\ell_{p_{i-1}}}^{\ell_{p_i}}\exp\left(-2s_i^2n_i \right) \leq \dfrac{\log(\psi T)}{2(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_i}^{2\alpha + 1}}.
\end{align*}

Hence, the probability that the changepoint is not detected by the first event is bounded by,
\begin{align*}
\dfrac{\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_i}^{2\alpha + 1}}.
\end{align*}

@@

>>>>

\begin{theorem}
\label{psbandit:Theorem:1}
The expected cumulative regret of ImpCPD algorithm is upper bounded by,
\begin{align*}
\E[R_t] &\leq \sum_{i = 1}^K\sum_{j=1}^{G}\bigg[ 1 
%%%%%%%%%%
+ \dfrac{4T^{\frac{3}{2}}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}}
%%%%%%%%%%
+ \Delta^{opt}_{i,c_j} + \dfrac{4\log(\psi T(\Delta^{opt}_{i,c_j})^4)}{2(\Delta^{opt}_{i,c_j})}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
& + \dfrac{2T^{\frac{3}{2}}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
&+ \Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{i,c_j})^2}
\bigg]
\end{align*}

where $\alpha,\psi$ are exploration parameters and $\Delta^{opt}_{i,c_{G+1}} = 0,\forall i\in\A$.
\end{theorem}

@@

\textbf{Step 2.(Define an optimality stopping phase $m_{i,c_j}$):} We define an optimality stopping phase $m_{i,c_j}$ for a sub-optimal arm $i\in\A$ as the first phase after which the arm $i$ is no longer pulled till the $c_j$-th changepoint is detected such that,

\begin{align*}
m_{i,c_j} = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{opt}_{i,c_j}}{4} \right\rbrace
\end{align*}

\textbf{Step 3.(Define a changepoint stopping phase $p_{i,c_j}$):} We define a changepoint stopping phase $p_{i,c_j}$ for an arm $i\in\A$ such that it is the first phase when the changepoint $c_j$ is detected such that,

\begin{align*}
p_{i,c_j} = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{chg}_{i,c_j}}{4} \right\rbrace
\end{align*}

\textbf{Step 4.(Regret for sub-optimal arm $i$ being pulled after $m_{i,c_j}$-th phase):} Note, that on or after the $m_{i,c_j}$-th phase a sub-optimal arm $i$ is not pulled anymore if these four conditions hold,

@@

Also, in the $m_{i,c_j}$-th phase if $n_i \geq \ell_{m_{i,c_j}} = \dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\epsilon_{m_{i,c_j}}}$ then we can show that,
\begin{align*}
s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\ell_{m_{i,c_j}}}} \leq \sqrt{\alpha\epsilon_{m_{i,c_j}}\dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{\log(\psi T\epsilon_{m_{i,c_j}}^2)}} \leq \dfrac{\Delta^{opt}_{i,c_j}}{4}.
\end{align*}

If indeed the four conditions in equation \ref{eq:arm-pull-opt} hold then we can show that in the $m_{i,c_j}$-th phase,

\begin{align*}
\hat{r}_{i,c_j} + s_i \leq {r}_{i,c_j} + 4s_i - 2s_i \leq {r}_{i,c_j} + \Delta^{opt}_{i,c_j} - 2s_i \leq {r}_{i*,c_j} - 2s_{i*} \leq \hat{r}_{i*,c_j} - s_{i*}
\end{align*}

Hence, the sub-optimal arm $i$ is no longer pulled on or after the $m_{i,c_j}$-th phase. Therefore, to bound the number of pulls of the sub-optimal arm $i$, we need to bound the probability of the complementary of the four events in equation \ref{eq:arm-pull-chg}.

@@

\begin{align*}
&\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} \geq  r_{i,c_j} + s_i \rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\exp\left(-2s_i^2n_i \right)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\exp\left(-2\dfrac{\alpha\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2n_i}n_i \right)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\dfrac{1}{\psi T\epsilon_{m_{i,c_j}}^2} \leq \sum_{m=0}^{m_{i,c_j}}\dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\epsilon_{m_{i,c_j}}}\dfrac{1}{(\psi T\epsilon_{m_{i,c_j}}^2)^{\alpha}} = \dfrac{\log(\psi T \epsilon_{m_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_{i,c_j}}^{2\alpha +1}}.
\end{align*}

@@

\begin{align*}
\sum_{m=0}^{m_{i,c_j}}\sum_{n_{i*} =1}^{\ell_{m_{i,c_j}}}\Pb\lbrace \hat{r}_{i*,c_j} \leq  r_{i*,c_j} - s_{i*} \rbrace &\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\exp\left(-2(s_{i*})^2n_{i*} \right)\leq \dfrac{\log(\psi T \epsilon_{m_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
\end{align*}

@@

\begin{align*}
\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace.
\end{align*}

But the event $\hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_i$ is possible only when the following three events occur, $\hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} , \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i$ and $r_{i*}-r_{i} < 2s_i $. But the third event will not happen for $n_i\geq \ell_{m_{i,c_j}}$. Proceeding as before, we can show that the probability of the remaining two events is bounded by,

\begin{align*}
&\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
&\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\left( \Pb\lbrace \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i \rbrace \bigcup \Pb\lbrace \hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} \rbrace \right)\leq 2\left(\dfrac{\log(\psi T \epsilon_{m_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\right)\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_{i,c_j}}^{2\alpha + 1}}.
\end{align*}

%\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}
Finally for the fourth event in equation \ref{eq:arm-pull-opt}, we can bound the probability of its complementary event by following the same steps as above,

\begin{align*}
\sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace r_{i,c_j} + s_i > r_{i*,c_j} + s_{i*} \rbrace \leq \dfrac{\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
\end{align*}

Combining the above four cases we can bound the probability that a sub-optimal arm $i$ will no longer be pulled on or after the $m_{i,c_j}$-th phase by,

\begin{align*}
\dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_{i,c_j}}^{2\alpha +1}} &\leq \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{M}\left(\dfrac{1}{\epsilon_{m}}\right)^{2\alpha +1} \overset{(a)}{\leq} \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\left(\dfrac{2(2^M - 1)}{2 - 1}\right)^{2\alpha +1} \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\overset{(b)}{\leq} \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\left(\sqrt{T}\right)^{2\alpha +1} = \dfrac{4\sqrt{T}\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi)^{\alpha}}.
\end{align*}

Here, in $(a)$ we use the standard geometric progression formula and in $(b)$ we substitute the value of $M=\dfrac{1}{2}\log_{2}\dfrac{T}{e}$. Bounding this trivially by $T\Delta^{opt}_{i,c_j}$ for each arm $i\in\A$ we get the regret suffered for arm $i$ after the $m_{i,c_j}$-th phase  as,

\begin{align*}
\sum_{i\in\A}\left( \dfrac{4T\Delta^{opt}_{i,c_j}\sqrt{T}\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi)^{\alpha}} \right) \leq \sum_{i\in\A}\left( \dfrac{4T^{\frac{3}{2}}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}} \right).
\end{align*}

%\begin{align*}
%\sum_{i\in\A}\left(\dfrac{4T\Delta^{opt}_{i,c_j}\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_{i,c_j}}^{2\alpha +1}}\right) \leq \sum_{i\in\A}\left(\dfrac{4T\Delta^{opt}_{i,c_j}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha +1}}{(\Delta^{opt}_{i,c_j})^{4\alpha +2}}\right).
%\end{align*}

\textbf{Step 5.(Regret for pulling the sub-optimal arm $i$ on or before $m_{i,c_j}$-th phase):} Either a sub-optimal arm gets pulled $\ell_{m_{i,c_j}}$ number of times till the $m_{i,c_j}$-th phase or after that the probability of it getting pulled is exponentially low (as shown in \textbf{step 4}). Hence, the number of times a sub-optimal arm $i$ is pulled till the $m_{i,c_j}$-th phase is given by,

\begin{align*}
n_i < \ell_{m_{i,c_j}} = \left\lceil \dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\epsilon_{m_{i,c_j}}} \right\rceil
\end{align*}

@@

\begin{align*}
\sum_{i\in\A}\Delta^{opt}_{i,c_j}\left\lceil \dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\epsilon_{m_{i,c_j}}} \right\rceil < \Delta^{opt}_{i,c_j}\left[ 1 + \dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\epsilon_{m_{i,c_j}}} \right] \leq \Delta^{opt}_{i,c_j}\left[ 1 + \dfrac{4\log(\psi T(\Delta^{opt}_{i,c_j})^4)}{2(\Delta^{opt}_{i,c_j})^2}\right].
\end{align*}

\textbf{Step 6.(Regret for not detecting changepoint $c_{j}$ for arm $i$ after the $p_{i,c_j}$-th phase):} Proceeding similarly as in \textbf{step 4} we can show that in the $p_{i,c_j}$-th phase for an arm $i$ if $n_{i}\geq\ell_{p_{i,c_j}}$ then,

\begin{align*}
s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2\ell_{p_{i,c_j}}}} \leq \sqrt{\alpha\epsilon_{p_{i,c_j}}\dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{\log(\psi T\epsilon_{p_{i,c_j}}^2)}} \leq \dfrac{\Delta^{chg}_{i,c_j}}{4}.
\end{align*}

@@

Indeed, we can show that if there is a changepoint at $c_j$ such that $r_{i,c_{j-1}} < r_{i,c_j}$ and if the first conditions in equation \ref{eq:arm-pull-chg} hold  in the $p_{i,c_j}$-th phase then,

\begin{align*}
\hat{r}_{i,c_{j-1}} + s_{i} \leq {r}_{i,c_{j-1}} + 4s_{i} - 2s_{i} \leq {r}_{i,c_{j-1}} + \Delta^{chg}_{i,c_j} -2s_{i} \leq {r}_{i,c_{j}} - 2s_i \leq \hat{r}_{i,c_{j}} - s_i.
\end{align*}

Conversely, for the case $r_{i,c_{j-1}} > r_{i,c_j}$ the second condition will hold for the $p_{i,c_j}$-th phase. Now, to bound the regret we need to bound the probability of the complementary of these two events. For the complementary of the first event in equation \ref{eq:arm-pull-chg} by using Chernoff-Hoeffding bound we can show that,

\begin{align*}
&\sum_{m=0}^{p_{i,c_j}}\sum_{n_i=1}^{\ell_{p_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_{j-1}} \geq  r_{i,c_{j-1}} + s_i \rbrace \leq \sum_{m=0}^{p_{i,c_j}}\sum_{n_i=1}^{\ell_{p_{i,c_j}}}\exp\left(-2s_i^2n_i \right)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\leq \sum_{m=0}^{p_{i,c_j}}\sum_{n_i=1}^{\ell_{p_{i,c_j}}}\exp\left(-2\dfrac{\alpha\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2n_i}n_i \right)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq \sum_{m=0}^{p_{i,c_j}}\sum_{n_i=1}^{\ell_{p_{i,c_j}}}\dfrac{1}{\psi T\epsilon_{p_{i,c_j}}^2} \leq \sum_{m=0}^{p_{i,c_j}}\dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2\epsilon_{p_{i,c_j}}}\dfrac{1}{(\psi T)^{\alpha}\epsilon_{p_{i,c_j}}^2} = \dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}}.
\end{align*}

@@

\begin{align*}
\sum_{m=0}^{p_{i,c_j}}\sum_{n_i=\ell_{p_{i-1}}}^{\ell_{p_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} \leq  r_{i,c_j} - s_i \rbrace &\leq \sum_{m=0}^{p_{i,c_j}}\sum_{n_i=\ell_{p_{i-1, c_j}}}^{\ell_{p_{i,c_j}}}\exp\left(-2s_i^2n_i \right) \leq \dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}}.
\end{align*}

Hence, the probability that the changepoint is not detected by the first event in equation \ref{eq:arm-pull-chg} is bounded by,
\begin{align*}
\dfrac{\log(\psi T)}{(\psi T \epsilon_{p_{i,c_j}}^2)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}}.
\end{align*}

@@

\begin{corollary}
\label{psbandit:corollary:1}
In the worst case scenario, when all the gaps are same, that is $\Delta^{opt}_{i,c_j}=\Delta^{chg}_{i,c_j}=\sqrt{\dfrac{K\log K}{T}}, \forall i\in\A,\forall j\in\G$ and setting $\alpha=\dfrac{1}{2}$ and $\psi = \dfrac{T^2}{K^2}$ then the worst case gap-independent regret bound of ImpCPD is given by,
